\chapter{Introduction}
\label{cha:introduction}
\thispagestyle{fancy}

In this report we define a person who rent out items as a \textit{\seller} and a
person who rent items as a \textit{\buyer}. We shall try to be consistent with 
this convention.

\section{Purpose and scope}
\label{sec:purpose-scope}
The project is about developing an online renting system (as a website), from
here on referred to as ORS. In the system it should be possible for users to
rent out items to other users for a small fee (possibly none) and a safety
deposit (in case of return of damaged items). When a user wants to rent a
provided item, the system should provide the contact information to the
providing user. The business case is to take a small percentage or amount from
the rental fee when providing the contact information.

Users should be able to search for specific items or item categories,
geographical locations, price ranges, etc. They should also be able to queue up
for a specific provided item (by another user) if it is already rented out or
multiple other people are interested in renting the item.

It should be possible to share what you are renting out on Facebook or Twitter.

A scenario could be a person, owning an electric saw, which he is not using, but
don't want to sell. He could then be interested in making some money off this
item, by renting it to people in his area (for example his home city Copenhagen,
or maybe in all of Sjælland, etc.). Instead of setting up fliers in his local
area (like in the local grocery store, local sports center, etc.) he puts the
item up on ORS because it is easy and fast. Now, people in need of such electric
saw contacts him without him doing anything but making the electric saw
available for renters.

The system is to be deployed and run on a cloud system like Amazon Cloud. It
should use an external payment system like PayPal.

\subsection{Scope}
\paragraph{Included}
\begin{itemize}
\item Supply items for rent
\item Search for items for rent
\item Requests items for rent
\item Billing + Deposits when renting
\item Tracking of items rented out (which user, living where)
\item Website handling the above
\end{itemize}

\paragraph{Excluded}
\begin{itemize}
\item Sales
\item Errors + Damage to items -- handling these cases
\item Hardware for the server -- we shall use a cloud solution.
\item Verification of transfers (how to verify an item is physically rented/given to a user and returned again).
\end{itemize}

\section{Audience}
\label{sec:audience}
The primary purpose of this document is communication between system architects
and system developers designing and building the actual system.
Further it can be used by sponsors and other stakeholders to get an overview of
the system.

\section{Status}
\label{sec:status}
The system is currently undergoing architectual design, as we are developing
the goals and ideas behind the system.

Our future plans include developing an architectual prototype, that shall show
our intentions and what external/internal components are required.

\section{Architectural design approach}
\label{sec:arch-design-appr}


