\chapter{System stakeholders and requirements}
\label{cha:syst-stak-requ}
\thispagestyle{fancy}

\section{Stakeholders}
\label{sec:stakeholders}
Here are the stakeholders, their interest and concerns about the system and whom their role is fulfilled by in ORS.
%\begin{table}[H]
\begin{center}
    \begin{longtable}[H]{| l |  p{6cm} | p{2cm} |}
    \hline
    \textbf{Stakeholder} & \textbf{Interest, needs and concerns} & \textbf{Held
        by} \\
    \hline
    Architect & Interested in the success of the system and is very concerned
        with the design and development. He is also concerned about the project
        fulfilling the found/given requirements. He needs a requirement
        specification and requires an assisting organization to carry
        out/develop the designed system. & ORS \\
    \hline
    Users &  Interested in a well-functioning and highly available product,
        with high standards on security in transactions of items. Their needs
        are based on the idea that they either provide items or would like to
        ``rent'' an item. They are primarily concerned with their personal
        security and the well-being of the rented item in question & Everyone \\
    \hline
    Acquirers & Interested in a successful and relative quick launch of the 
        system along with the business model of the system and eventual 
        marketing and advertising. & Possible investors, ORS owners \\
    \hline
    Assessors & Interested mainly around the legality and validity of the
        protocols surrounding the system. Their needs are in the area of
        transparency and documentation of the system, such that the are able to
        assess the system. & Lawyers and ORS Legal team, maybe external
        accountants\\
    \hline
    Communicators & Interested in the creation of the license agreements and 
        rental contracts for the site. & Lawyers and ORS Legal team\\
    \hline
    Developers & Interested in the design of the software system and is 
        concerned with the modularity (that the system is easy to 
        maintain/expand) and performance. & ORS Development team\\
    \hline
    Maintainers & Interested in the modularity of the system, defining how easy
        the system is to fix and expand, along with the platform (here Amazon 
        Cloud) the system is to be runned on. & ORS Admins \\
    \hline
    Production Engineers & Interested in the different parts of the system 
        (including external systems like Paypal), the ease of deployment of the
        system and the platform it runs on. & Amazon and ORS Admins\\
    \hline
    Suppliers & Interested in the use and integration of their external systems
        (for example the billing system of Paypal and the Amazon cloud). 
        & Paypal, Amazon\\
    \hline
    Support Staff & Interested in the functionality and stability of the system,
        along with the usability; how easy it is to administrate users and to 
        use the site. & ORS Admins \\
    \hline
    System Administrators & Interested in the stability and accessibility to 
        the system (when using Amazon cloud, what kind of access do we have to 
        it and how much control do we have) and the platform/hardware it is run
        on, giving and idea of how easy it is to fix eventual problems, with 
        respect to both software and hardware. & ORS Admins and Amazon \\
    \hline
    Testers & Interested in early access to the system along with the stability
        and functionality of the system, which they test. 
        & Possible early users\\
    \hline
  \end{longtable}
\end{center}
%\end{table}


\section{Overview of requirements}\label{sec:overv-requ}
\begin{center}
  \begin{tabular}[h]{| l |  l |}
    \hline
    \textbf{Reference} & \textbf{Requirement description} \\
    \hline
    R1 & \Seller creating an item to rent out (usability)\\
    \hline
    R2 & \Buyer finding and renting item (usability)\\
    \hline
    R3 & Admin removing item from site (usability)\\
    \hline
    R4 & Many \buyers try to rent same item (usability, accessibility)\\
    \hline
    Q1 & A user tries to access an item under heavy load (performance, availability)\\
    \hline
    Q2 & A user tries to access the site without valid credentials (security)\\
    \hline
    Q3 & A user rents an item under normal load (performance, security)\\
    \hline
  \end{tabular}
\end{center}

\section{System scenarios}
\label{sec:system-scenarios}
The following two sections tries to describe scenarios related to the above
requirements. Their role is to dig into the requirements, and make them more
``alive''.

\subsection{Functional scenarios}
\label{sec:functional-scenarios}
The scenarios concerning the functionality of the system are listed and
described below. The template is the one from \cite{rozanski2011software}
chapter 10.

\begin{description}
    \item[Overview] R1 - \Seller creating an item in the system
    \item[System state] The user is authenticated and logged in
    \item[System environment] The environment has no issues
    \item[External stimulus] The user submits a request to add an item for rent
        in the database
    \item[Required system response] The system shall start processing the
        incoming record and tell the user, that their item will be added
        shortly.
\end{description}

\begin{description}
    \item[Overview] R2 - \Buyer finds and rents an item
    \item[System state] The system contains at least one item, that is
        available for renting out.
    \item[System environment] The system is in its normal environment, and the
        person renting out, is ready to deliver.
    \item[External stimulus] The user request the system to facilitate a
        ``rent''
    \item[Required system response] The system shall notify the person renting
        out about interest, afterwards it shall notify the interested party on
        the availability of the requested item.
\end{description}

\begin{description}
    \item[Overview] R3 - Administrator removes an item from the site
    \item[System state] The system contains at least one item, that has a
        status of ``available for renting out''.
    \item[System environment] The system is in its normal environment.
    \item[External stimulus] The administrator deletes and item from the system 
    \item[Required system response] The system shall notify the \seller about
        the deletion, furthermore the deleted item shall not be shown on-site
        to any users.
\end{description}

\begin{description}
    \item[Overview] R4 - Many \buyers try to rent the same item
    \item[System state] The system contains at least one item, that has a
        status of ``available for renting out''. And at least 2 \buyers.
    \item[System environment] The system is in its normal environment.
    \item[External stimulus] At least 2 \buyers try to access the same item and
        rent it at the ``same'' time.
    \item[Required system response] The system shall notify the \seller about
        the interest, furthermore \buyers shall be notified of the competition
        for the scarce resource.
\end{description}

\subsection{System quality scenarios}
\label{sec:syst-qual-scen}
This section closely mimics the previous, but concerns the quality scenarios
instead.

\begin{description}
    \item[Overview] Q1 - A user tries to access an item while the system is
        under heavy load.
    \item[System state] The system is in its normal working condition, with at
        least one user signed up
    \item[System environment] The system is working correctly and has 10.000
        active users pr minute
    \item[Environment change] A spike in traffic, at around 100.000 users pr
        minute, accessing the system.
    \item[Required system behavior] The system is expected to scale within the
        first 10 seconds, and return error pages to less than 10.000 users.
\end{description}

\begin{description}
    \item[Overview] Q2 - A user tries to access the site without valid
        credentials.
    \item[System state] The system has at least one users signed up.
    \item[System environment] The system is handling its average 10.000 users pr
        minute, the system' environment is functioning normally.
    \item[Environment change] The user tries to access the frontpage, a
        subsequent item-page and then tries to rent an item.
    \item[Required system behavior] The system is expected to present both
        frontpage and item-page, but give an error/warning when the
        unauthenticated user tries to rent an item.
\end{description}

\begin{description}
    \item[Overview] Q3 - A user rents an item under normal load
    \item[System state] The system has at least two users has signed up, one
        renting out another renting.
    \item[System environment] The system is handling its average 10.000 users pr
        minute, the system' environment is functioning normally.
    \item[Environment change] A user asks to rent an item
    \item[Required system behavior] The system is expected to respond to
        incoming requests in less than 0.1 second
\end{description}

\begin{description}
    \item[Overview] Q4 - Availability of Services (availabillity and uptime)
    \item[System environment] The deployment environment is working normally
    \item[Environment change] ORS site (server) becomes unavailable for hardware or software reasons
    \item[Required system behavior] Service is reestablished. Availabillity over a year is 95\%.
\end{description}

\begin{description}
    \item[Overview] Q5 - A user tries to change an items data
    \item[System environment] The system is working normally
    \item[Environment change] A user is authenticated and tries to change the
        data for an item, that the user does not own.
    \item[Required system behaviour] Deny the change
\end{description}
